The Efficient Handling of Guards in the Design of RPython's Tracing JIT

### 2012-08-14 talk/vmil2012/paper.tex
Settle for front- and backend

The set of central concepts upon which this work is based is described in
Section~\ref{sec:Background}, such as the PyPy project, the RPython language
and its meta-tracing JIT. Based on these concepts in Section~\ref{sec:Resume
Data} we proceed to describe for RPython's tracing JIT the details of guards in
the frontend\bivab{better term for this?} related to recording and storing the
information required to rebuild the interpreter state in case of a guard
failure. Once the frontend has traced and optimized a loop it invokes the
backend to compile the operations to machine code, Section \ref{sec:Guards in
the Backend} describes the low-level aspects of how guards are implemented in
the JIT-backend. The frequency of guards and the overhead associated with the
implementation described in this paper is discussed in
Section~\ref{sec:evaluation}. Section~\ref{sec:Related Work} presents an
overview about how guards are treated in the context of other just-in-time
compilers. Finally Section~\ref{sec:Conclusion} summarizes our conclusions and
gives an outlook on further research topics.

>>>>

The set of central concepts upon which this work is based is described in
Section~\ref{sec:Background}, such as the PyPy project, the RPython language
and its meta-tracing JIT. Based on these concepts in Section~\ref{sec:Resume
Data} we proceed to describe for RPython's tracing JIT the details of guards in
the frontend related to recording and storing the
information required to rebuild the interpreter state in case of a guard
failure. Once the frontend has traced and optimized a loop it invokes the
backend to compile the operations to machine code, Section \ref{sec:Guards in
the Backend} describes the low-level aspects of how guards are implemented in
the machine specific JIT-backend. The frequency of guards and the overhead associated with the
implementation described in this paper is discussed in
Section~\ref{sec:evaluation}. Section~\ref{sec:Related Work} presents an
overview about how guards are treated in the context of other just-in-time
compilers. Finally Section~\ref{sec:Conclusion} summarizes our conclusions and
gives an outlook on further research topics.
